---
title: ""
output: 
  html_document:
    theme:  united
    css: interesting_finding.css
    number_sections: FALSE
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
#install.packages("DT")
library(DT)
library(tidyverse)
library(httr)
library(plotly)
library(knitr)
library(modelr)
# library(HH)

theme_set(theme_bw())
```

<a href="https://github.com/jackyan0320/p8105_final_project" class="github-corner" aria-label="View source on Github"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#dd4814; color:#fff; position: absolute; top: 50; border: 0; right: 0;" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}} </style>

```{r data process chuck, message=F, warning=F, include=F}
organ =
  read_csv("./data/organ.csv") %>% 
  filter(county != "TOTAL NYS") 
demo_ny = 
  read.csv("./data/ahrf_select_data.csv") %>% as.tibble() %>% 
  janitor::clean_names() %>% 
  rename(county = county_name) 
```

<div style="margin-bottom:50px;">
</div>

# County characteristics {.tabset .tabset-fade .tabset-pills}

<div style="margin-bottom:30px;">
</div>

## Regression analysis

<div style="margin-bottom:20px;">
</div>

When analyzing county level factors, we limited data to September, 2018. 

```{r message = F, warning= F, echo = FALSE}
organ_2018_09 <- 
  organ %>%
  filter(date == '2018-09-01') %>% 
  rename(percent_enrolled = eligible_population_enrolled)

demo_ny <-  
  read.csv("data/ahrf_select_data.csv") %>% 
  as.tibble() %>% 
  rename(county = county_name)

combined_df <- 
  inner_join(by = 'county', organ_2018_09, demo_ny) %>%
  select(county, opo, population_18_estimate, registry_enrollments, percent_enrolled,
         standardzd_per_capita_medcr_cost_fee_for_service_2015:percent_educ_hlth_care_soc_asst_2011_15) %>% 
  mutate(opo = fct_relevel(opo, "New York Organ Donor Network")) %>% 
  mutate(
    pop_total_2015 = (pop_total_female_2015 + pop_total_male_2015),
    percent_male_2015 = round(100 * (pop_total_male_2015 / pop_total_2015), 2),
    percent_white_2015 = (pop_white_female_2015 + pop_white_male_2015) / pop_total_2015,
    percent_white_2015 = round(100 * percent_white_2015, 2),
    percent_black_2015 = (pop_black_african_amer_female_2015 + 
                            pop_black_african_amer_male_2015) / pop_total_2015,
    percent_black_2015 = round(100 * percent_black_2015, 2),
    percent_asian_2015 = (pop_asian_female_2015 + pop_asian_male_2015) / pop_total_2015,
    percent_asian_2015 = round(100 * percent_asian_2015, 2),
    percent_medicare_enrollment_2015 = round((medicare_enrollment_aged_tot_2015 * 100 / pop_total_2015), 2)) %>% 
  select(-(pop_total_male_2015:pop_asian_female_2015), 
                -population_estimate_2016, 
                -medicare_enrollment_aged_tot_2015) %>% 
  select(county, percent_enrolled, everything())

regression_df <- 
  combined_df %>% 
  select(-county) %>% 
  rename(pop_18 = population_18_estimate, 
         reg_enroll = registry_enrollments, 
         medcr_fee_2015 = standardzd_per_capita_medcr_cost_fee_for_service_2015, 
         percent_hs_diploma = percent_persons_25_w_hs_diploma_2011_15,
         percent_college = percent_persons_25_w_4_yrs_college_2011_15,
         percent_soc_asst = percent_educ_hlth_care_soc_asst_2011_15, 
         pop_2015 = pop_total_2015, 
         percent_medcr_2015 = percent_medicare_enrollment_2015)
```

The final model included the following variables: organ procurement organization, percent of population enrolled in Medicare, percent of county that is males, percent of county that is White, percent of adults over 25 with a high school diploma, percent of adults over the age of 25 that have a college degree, and an interaction between the percent of the county that is white and the percent of adults over 25 with a high school diploma.

```{r final county model, echo = FALSE}
county_final <- regression_df %>%  
  lm(percent_enrolled ~ opo + percent_medcr_2015 + percent_male_2015 + percent_white_2015*percent_hs_diploma +
       percent_college, data = .)

county_final %>%
  broom::tidy() %>% 
  kable(digits = 3)
```

We found that type of OPO that conducts the registration affects registration rate. Percentage of medicare enrollment, percentage of persons finishing high school education and finishing 4-year college education are positively associated with registration rate. This finding agrees with our hypothesis. Also, the sex `male` and race `white` are positively associated with registration rate. 


Here we compare the candidate models

|Model       |Adjusted r-squared  | AIC         |
|-------------|-----------------------|---------|
|Final model        |0.81  |331.97            |
|Model 1      |     0.76  |   345.46     |
|Model 2      |  0.74     |     348.62  |



```{r bootstrap, eval = FALSE}
bootstrap_df <-  
  regression_df %>% 
  modelr::bootstrap(n = 100) %>% 
  mutate(
    model_1 = purrr::map(strap, ~lm(percent_enrolled ~ opo + percent_hs_diploma + percent_college + percent_male_2015 +
                                      percent_asian_2015 + percent_medcr_2015, data = .x)),
    model_2 = purrr::map(strap, ~lm(percent_enrolled ~ opo + percent_medcr_2015 + percent_male_2015 +
                                      percent_white_2015 + percent_hs_diploma + percent_college, data = .x)),
    model_3 = purrr::map(strap, ~lm(percent_enrolled ~ opo + percent_medcr_2015 + percent_male_2015 +
                                      percent_white_2015*percent_hs_diploma + percent_college, data = .x))) 

bootstrap_df %>% 
  mutate(
    result_1 = purrr::map(model_1, broom::tidy),
    result_2 = purrr::map(model_2, broom::tidy),
    result_3 = purrr::map(model_3, broom::tidy)) %>% 
  select(-strap, -(model_1:model_3))  %>% 
  gather(key = model, value = result, result_1:result_3) %>% 
  unnest() %>% 
  filter(term != "(Intercept)") %>% 
  group_by(model, term) %>% 
  summarize(boot_se = sd(estimate)) %>% 
  spread(key = model, value = boot_se) %>% 
  kable()
```

```{r cross validation}
set.seed(10)

cv_df <- crossv_mc(regression_df, 100) 

cv_df <-  
  cv_df %>% 
  mutate(
    model_1 = purrr::map(train, ~lm(percent_enrolled ~ opo + percent_hs_diploma + percent_college + percent_male_2015 +
                                      percent_asian_2015 + percent_medcr_2015, data = .x)),
    model_2 = purrr::map(train, ~lm(percent_enrolled ~ opo + percent_medcr_2015 + percent_male_2015 +
                                      percent_white_2015 + percent_hs_diploma + percent_college, data = .x)),
    model_3 = purrr::map(train, ~lm(percent_enrolled ~ opo + percent_medcr_2015 + percent_male_2015 +
                                      percent_white_2015*percent_hs_diploma + percent_college, data = .x))) %>% 
  mutate(rmse_1 = purrr::map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_2 = purrr::map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = purrr::map2_dbl(model_3, test, ~rmse(model = .x, data = .y))) %>% 
  select(-train, -test, -(model_1:model_3)) %>% 
  gather(key = model, value = rmse, rmse_1:rmse_3)

cv_df %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  labs(x = "Model", 
       y = "RMSE")
```

<br />
<br />
<br />
<br />

<div style="margin-bottom:50px;">
</div>

<div style="margin-bottom:20px;">
</div>


      