---
title: "website_plots"
author: "Alina Levine"
date: "November 30, 2018"
output: html_document
---




```{r}

library(tidyverse)
library(ggplot2)
library(plotly)



```


#Plotting Eligible Percent Enrolled Versus Population

```{r}
organ = read_csv("data/organ_spline.csv") 


organ %>% 
  filter(date == as.Date("2018-09-01")) %>% 
  filter(county!= "TOTAL NYS") %>%
  plot_ly(x = ~population_18_estimate, y = ~eligible_population_enrolled, type = "scatter", mode = "markers",
          alpha = 0.5, 
          text = ~county)

#If you have a county that has a higher population of people, a higher percent enrolled is more helpful in terms of number of organs than if a county has a lower population of people, so New York should be taking advantage of larger counties, but this plot shows that larger counties tend to have lower percentages of eligible people enrolled. 

#smaller counties have higher percentages enrolled

  
```


#Difference of Slope: July 2012


```{r}


diff_diff_organ_2012 = organ %>%
  filter(date == as.Date("2014-07-01") | date == as.Date("2012-07-01") | date == as.Date("2010-07-01")) %>%
  select(county, date, eligible_population_enrolled) %>%
  group_by(county) %>%
  spread(value = eligible_population_enrolled, key = date) %>%
  janitor::clean_names() %>%
  mutate(slope_2012_2010 = (x2012_07_01-x2010_07_01)/as.integer(as.Date("2012-07-01")-as.Date("2010-07-01")),
         slope_2014_2012 = (x2014_07_01-x2012_07_01)/as.integer(as.Date("2014-07-01")-as.Date("2012-07-01")),
         slope_diff = slope_2014_2012-slope_2012_2010) %>%
  ungroup() %>%
  mutate(county = fct_reorder(county, slope_diff)) %>%
  mutate(is_total_nys = ifelse(county == "TOTAL NYS", 1, 0))

diff_diff_organ_ny_2012 = filter(diff_diff_organ, county %in% c("TOTAL NYS"))

library(ggrepel)

  ggplot(diff_diff_organ_2012, aes(x = county, y = slope_diff)) +
    geom_point() +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(legend.position = "none") +
    geom_text_repel(data = diff_diff_organ_ny_2012, 
                    aes(x = county, 
                        y = slope_diff, 
                        label = county), nudge_x = -2.5, nudge_y = .001) +
    labs(title = "Slope Change After 2012 Policy",
         y = "Slope Change")
    

```

Based on this plot, it appears that most counties' slopes actually decreased following the 2012 law (I used the two year period before and after). The percent enrolled countinues to increase, but it does so at a smaller rate. 


#Difference in Slope: February 2017

```{r}

diff_diff_organ_2017 = organ %>%
  filter(date == as.Date("2018-09-01") | date == as.Date("2017-02-01") | date == as.Date("2015-07-01")) %>%
  select(county, date, eligible_population_enrolled) %>%
  group_by(county) %>%
  spread(value = eligible_population_enrolled, key = date) %>%
  janitor::clean_names() %>%
  mutate(slope_2017_2015 = (x2017_02_01-x2015_07_01)/as.integer(as.Date("2017-02-01")-as.Date("2015-07-01")),
         slope_2018_2017 = (x2018_09_01-x2017_02_01)/as.integer(as.Date("2018-09-01")-as.Date("2017-02-01")),
         slope_diff = slope_2018_2017-slope_2017_2015) %>%
  ungroup() %>%
  mutate(county = fct_reorder(county, slope_diff)) %>%
  mutate(is_total_nys = ifelse(county == "TOTAL NYS", 1, 0))

diff_diff_organ_ny_2017 = filter(diff_diff_organ_2017, county %in% c("TOTAL NYS"))


  ggplot(diff_diff_organ_2017, aes(x = county, y = slope_diff)) +
    geom_point() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(legend.position = "none") +
    geom_text_repel(data = diff_diff_organ_ny_2017, 
                    aes(x = county, 
                        y = slope_diff, 
                        label = county), nudge_x = -2.5, nudge_y = .01) +
    labs(title = "Slope Change After 2017 Policy",
         y = "Slope Change")
    


```

Almost all the slopes increase after 2017. NY county, one of the larger counties in NY, is one of the 7 counties that has a decreasing average slope. 



