---
title: ""
output: 
  html_document:
     theme:  united
     includes:
        after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("DT")
library(DT)
library(tidyverse)
```

<div style="margin-bottom:30px;">
</div>

# About Our data

<div style="margin-bottom:20px;"> </div>

### This is a page we describe Our Data. For our exploratory study we used two datasets.

<div style="margin-bottom:20px;"> </div>

##### * Data from [New York State organ donation data](https://health.data.ny.gov/Health/Donate-Life-Organ-and-Tissue-Donor-Registry-Enroll/sqk8-8a2h/data?fbclid=IwAR0DjHPMd3up76Cq1bMH0z12f_vr4rLz5YwtMPcT2kc_a5nP-nVJlDEinNE) is used extract registry porportion of each county to do the model fitting.

##### * Data from ... is used to extract the demographic data of the New York State.

<div style="margin-bottom:50px;"> </div>

### The following chart is a brief overview of the New York State organ donation data.

<div style="margin-bottom:50px;"> </div>

```{r ,include=FALSE}
organ = read_csv("data/organ.csv")
organ_tidy = 
  organ %>% 
  separate(location, c("lat", "long"), sep = ",") %>% 
  mutate(long = str_replace(long, "\\)", ""),
         long = as.numeric(long)) %>% 
  mutate(lat = str_replace(lat, "\\(", ""),
         lat = as.numeric(lat)) %>% 
  select(date, county, eligible_population_enrolled, population_18_estimate, registry_enrollments, opo) %>% 
  rename(registry_proportion = eligible_population_enrolled) %>% 
  mutate(opo = as.factor(opo),
         county = as.factor(county)) %>% 
  rename(OPO = opo)
```
<div class="cd-fixed-bg cd-fixed-bg--1"> 
</br>
</div>

 
```{r echo=FALSE, }
donor_share_time_compare = read.csv("data/state_donor_share.csv") %>%
  janitor::clean_names() %>%
  rename(state = x)

datatable(organ_tidy, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T, autoWidth = TRUE) )
```
     
