---
title: ""
output: 
  html_document:
    theme:  united
    css: website_explore_page.css
    number_sections: FALSE
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")
#install.packages("DT")
library(DT)
library(tidyverse)
library(httr)
library(plotly)
library(knitr)
library(modelr)
library(ggrepel)
# library(HH)

theme_set(theme_bw())
```

<a href="https://github.com/jackyan0320/p8105_final_project" class="github-corner" aria-label="View source on Github"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#dd4814; color:#fff; position: absolute; top: 50; border: 0; right: 0;" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}} </style>

```{r data process chuck, message=F, warning=F, include=F}
organ =
  read_csv("./data/organ.csv") %>% 
  filter(county != "TOTAL NYS") 

demo_ny = 
  read.csv("./data/ahrf_select_data.csv") %>% as.tibble() %>% 
  janitor::clean_names() %>% 
  rename(county = county_name) 
```


```{r message = F, warning= F, echo = FALSE}
organ_2018_09 <- 
  organ %>%
  filter(date == '2018-09-01') %>% 
  rename(percent_enrolled = eligible_population_enrolled)

demo_ny <-  
  read.csv("data/ahrf_select_data.csv") %>% 
  as.tibble() %>% 
  rename(county = county_name)

combined_df <- 
  inner_join(by = 'county', organ_2018_09, demo_ny) %>%
  select(county, opo, population_18_estimate, registry_enrollments, percent_enrolled,
         standardzd_per_capita_medcr_cost_fee_for_service_2015:percent_educ_hlth_care_soc_asst_2011_15) %>% 
  mutate(opo = fct_relevel(opo, "New York Organ Donor Network")) %>% 
  mutate(
    pop_total_2015 = (pop_total_female_2015 + pop_total_male_2015),
    percent_male_2015 = round(100 * (pop_total_male_2015 / pop_total_2015), 2),
    percent_white_2015 = (pop_white_female_2015 + pop_white_male_2015) / pop_total_2015,
    percent_white_2015 = round(100 * percent_white_2015, 2),
    percent_black_2015 = (pop_black_african_amer_female_2015 + 
                            pop_black_african_amer_male_2015) / pop_total_2015,
    percent_black_2015 = round(100 * percent_black_2015, 2),
    percent_asian_2015 = (pop_asian_female_2015 + pop_asian_male_2015) / pop_total_2015,
    percent_asian_2015 = round(100 * percent_asian_2015, 2),
    percent_medicare_enrollment_2015 = round((medicare_enrollment_aged_tot_2015 * 100 / pop_total_2015), 2)) %>% 
  select(-(pop_total_male_2015:pop_asian_female_2015), 
                -population_estimate_2016, 
                -medicare_enrollment_aged_tot_2015) %>% 
  select(county, percent_enrolled, everything())

regression_df <- 
  combined_df %>% 
  select(-county) %>% 
  rename(pop_18 = population_18_estimate, 
         reg_enroll = registry_enrollments, 
         medcr_fee_2015 = standardzd_per_capita_medcr_cost_fee_for_service_2015, 
         percent_hs_diploma = percent_persons_25_w_hs_diploma_2011_15,
         percent_college = percent_persons_25_w_4_yrs_college_2011_15,
         percent_soc_asst = percent_educ_hlth_care_soc_asst_2011_15, 
         pop_2015 = pop_total_2015, 
         percent_medcr_2015 = percent_medicare_enrollment_2015)
```

<div style="margin-bottom:50px;">
</div>

# Exploratory plots {.tabset .tabset-fade .tabset-pills}

<div style="margin-bottom:30px;">
</div>

## Enroll Number vs State Pop

<div style="margin-bottom:20px;">
</div>

When analyzing 

<div style = "">
```{r message = F, warning= F}
lowest_3_counties = organ %>% 
  filter(date == as.Date("2018-09-01")) %>% 
  filter(county != "TOTAL NYS") %>%
  arrange(eligible_population_enrolled) %>%
  top_n(n = -3, eligible_population_enrolled)

trend_1 = 
  organ %>%
  # only use data after 2017-10-01
  filter(date == '2018-09-01') %>% 
  mutate(text_label = str_c("Eligible pop:", population_18_estimate, '\nregistry_enrollments: ',
                            registry_enrollments, "\nCounty:", county, "\ndate:", date)) %>% 
  plot_ly(x = ~population_18_estimate, 
          y = ~registry_enrollments, 
          type = "scatter", 
          mode = "markers",
          color = ~county,
          text = ~text_label) 
trend_1 

plot_enrollments_population = 
  organ %>%
  filter(date == '2018-09-01') %>% 
  ggplot(aes(x = population_18_estimate, y = registry_enrollments)) +
  geom_point(aes(group = county)) +
  geom_smooth(method = 'auto', se = FALSE) +
  theme_bw() 

ggplotly(plot_enrollments_population)

```

</div>

## Percent Enroll vs State Pop

<div style="margin-bottom:20px;">
</div>



<div style = ""> 
```{r message = F, warning= F}

trend_2 = 
  organ %>%
  # only use data after 2017-10-01
  filter(date == '2018-09-01') %>% 
  mutate(text_label = str_c("Eligible pop:", population_18_estimate, '\nregistry_enrollments: ',  registry_enrollments, "\nCounty:", county, "\ndate:", date)) %>% 
  plot_ly(x = ~population_18_estimate, 
          y = ~eligible_population_enrolled, 
          type = "scatter", 
          mode = "markers",
          color = ~county,
          text = ~text_label) %>% 
  add_annotations(x = lowest_3_counties$population_18_estimate , 
                  y = lowest_3_counties$eligible_population_enrolled, 
                  text = lowest_3_counties$county) %>%
  layout(xaxis = list(title = "Population 18 and Over"),
         yaxis = list(title = "Percent of Eligible Population Enrolled"))
trend_2


```

The counties with the lowest enrollment tend to be in the New York City area. The larger counties have lower registration rates, which is problematic, since larger counties have the potential to provide the most organs. 

</div>

<div style = "display :block; margin-bottom:120%;"></div>

## State Comparison

<div style="margin-bottom:20px;">
</div>


```{r state comparison, echo = FALSE, message = FALSE, warning =FALSE}
read_csv("data/state_donor_share.csv") %>%
  janitor::clean_names() %>%
  ggplot(aes(x = year, y = donor_designation_share, color = state)) +
    geom_point() +
    geom_smooth() +
    labs(title = "State Percentage Enrolled Comparison",
         x = "Year",
         y = "Percent Eligible Enrolled")
```
  
This plot includes states near New York. New York's percentage of eligible people enrolled in 2017 was 8 percentage points lower than the next lowest of these states.  



## Registration Over Time 

The registry enrollments showed a generally increasing trend across the years. However, note that there is a sudden change in registry enrollments on 2009-06-01 and 2017-10-1. Curiously, the enrollment even declined for some counties on 2017-10-1, which indicates an aspect of limitation of the dataset.

```{r}
county_enrollment_plot = 
  organ %>% 
  ggplot(aes(x = date, y = registry_enrollments, color = county)) +
    geom_line() +
    labs(x = "Date", 
         y = "Persons enrolled", 
         title = "Registry enrollments across time") + 
  viridis::scale_color_viridis(discrete = TRUE)

ggplotly(county_enrollment_plot)
```

<div style = "float: right; width: 50%"> 
</div>

This plot shows the trend of registration rate from 2008 to 2018 for counties in New York State. Note that the registration rates for Counties Cattauragus and St Lawrence were not updated throughout the years.
     
```{r message = F, warning= F}
county_enrollment_rate_plot = 
  organ %>% 
  ggplot(aes(x = date, y = eligible_population_enrolled, color = county)) +
    geom_line() +
    labs(x = "Date", 
         y = "% Persons enrolled", 
         title = "Registration rate across time") + 
  viridis::scale_color_viridis(discrete = TRUE)

ggplotly(county_enrollment_rate_plot)
```

There was a huge leap in pupulation_18_estimate at 2017-10-01 among almost all the counties
</div>   




